---
title: "XYZ: The Name Of Your Course"
format: 
  gfm:
    df-print: kable
self-contained: true
---

This webpage contains all materials required for the course XYZ.

The materials on this website are [CC-BY-4.0](https://creativecommons.org/licenses/by/4.0/) licensed.

![cc](https://mirrors.creativecommons.org/presskit/icons/cc.svg) ![by](https://mirrors.creativecommons.org/presskit/icons/by.svg)

## Syllabus

You can find the course syllabus as a web page [here](syllabus.html) or as a pdf [here](syllabus.pdf). The course schedule with required reading materials is in the syllabus as well, specifically [here](./syllabus#class-schedule).

## Lectures
```{r}
#| echo: false
readxl::read_xlsx("course_schedule.xlsx") |>
  dplyr::mutate(Topic = ifelse(!is.na(URL), glue::glue("[{Title}]({URL})"), Title), .keep = "unused") |> 
  dplyr::relocate(Topic, .after = Date) |> 
  dplyr::filter(Type == "Lecture") |>
  dplyr::select(Week, Date, Topic)
```

## Labs
```{r}
#| echo: false
readxl::read_xlsx("course_schedule.xlsx") |>
  dplyr::mutate(Topic = ifelse(!is.na(URL), glue::glue("[{Title}]({URL})"), Title), .keep = "unused") |> 
  dplyr::filter(Type == "Lab") |>
  dplyr::select(Week, Date, Topic)
```

## Deadlines
```{r}
#| echo: false
readxl::read_xlsx("course_schedule.xlsx") |>
  dplyr::mutate(Topic = ifelse(!is.na(URL), glue::glue("[{Title}]({URL})"), Title), .keep = "unused") |> 
  dplyr::relocate(Topic, .after = Date) |> 
  dplyr::filter(Type %in% c("Deadline", "Exam", "Resit")) |>
  dplyr::select(Week, Date, Topic)
```